asc_file_database

### 2020-01-17 src/asc_file_database_combined_files.Rmd
amo and nao added, model completed

```{r base list or ascii layers}
ascyears <- as.character(c("1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015")) 
#unyears <- paste0("X", unyears) #this adds an X to each year to match with raster naming
ascmonths <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

asclayerall <- crossing(ascyears, ascmonths)
asclayerall$stackname <- paste0("st", asclayerall$ascyears, asclayerall$ascmonths) #this creates the name of the stack that will be used
asclayerall$temp_depth <- NA
asclayerall$chl_depth <- NA
asclayerall$o2_depth <- NA
asclayerall$salinity_depth <- NA
# asclayerall$nao_sample <- NA
# asclayerall$nao_prev <- NA
# asclayerall$nao_winter <- NA
# asclayerall$amo_sample <- NA
# asclayerall$amo_prev <- NA
# asclayerall$amo_winter <- NA

@@

myr <- 2014 #!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

@@

tempvar <- "temp.asc"
chlvar <- "chl.asc"
o2var <- "o2.asc"
salvar <- "salinity.asc"
# naosamplevar <- "naosample"
# amosamplevar <- "amosample"
# naoprevvar <- "naoprev"
# amoprevvar <- "amoprev"
# naowintervar <- "naowinter"
# amowintervar <- "amowinter"
# surfacevar <- "0.50576"

@@

        if (ascyear == year & ascmonth == month & ascvar == tempvar){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var){
          asclayer$o2_depth[i] <- ascfile
        # } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
        #   asclayer$nao_sample[i] <- ascfile
        # } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
        #   asclayer$amo_sample[i] <- ascfile
        # } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
        #   asclayer$nao_prev[i] <- ascfile
        # } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
        #   asclayer$amo_prev[i] <- ascfile
        # } else if(ascyear == year & ascvar == naowintervar){
        #   asclayer$nao_winter[i] <- ascfile
        # } else if(ascyear == year & ascvar == amowintervar){
        #   asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, paste0("../data/env/test-comb/asc_layerlist", myr, ".csv"), row.names = TRUE)
}
```

>>>>

```{r base list or ascii layers}
ascyearslist <- as.character(c("1998", "1999", "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014")) 
#unyears <- paste0("X", unyears) #this adds an X to each year to match with raster naming
ascmonths <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

asclayerall <- crossing(ascyears, ascmonths)
asclayerall$stackname <- paste0("st", asclayerall$ascyears, asclayerall$ascmonths) #this creates the name of the stack that will be used
asclayerall$temp_depth <- NA
asclayerall$chl_surface <- NA
asclayerall$o2_depth <- NA
asclayerall$salinity_depth <- NA
asclayerall$nao_sample <- NA
asclayerall$nao_prev <- NA
asclayerall$nao_winter <- NA
asclayerall$amo_sample <- NA
asclayerall$amo_winter <- NA

@@

for (ny in 1:length(ascyearslist)){
  myr <- ascyearslist[ny] #!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

@@

tempvar <- "temp.asc"
chlvar <- "chl.asc"
o2var <- "o2.asc"
salvar <- "salinity.asc"
naosamplevar <- "naosample.asc"
amosamplevar <- "amosample.asc"
naoprevvar <- "naoprev.asc"
naowintervar <- "naowinter.asc"
amowintervar <- "amowinter.asc"
surfacevar <- "0.50576"

@@

        if (ascyear == year & ascmonth == month & ascvar == tempvar){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var){
          asclayer$o2_depth[i] <- ascfile
         } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
           asclayer$nao_sample[i] <- ascfile
         } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
           asclayer$amo_sample[i] <- ascfile
         } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
           asclayer$nao_prev[i] <- ascfile
         } else if(ascyear == year & ascvar == naowintervar){
           asclayer$nao_winter[i] <- ascfile
         } else if(ascyear == year & ascvar == amowintervar){
           asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, paste0("../data/env/test-comb/asc_layerlist", myr, ".csv"), row.names = TRUE)
}
}
```

### 2020-01-17 src/comb-maxent.Rmd
amo and nao added, model completed

select month
```{r month of interest -change}
mthna <- "mar"
mthno <- "3"
```

@@

@@

```{r}
marvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
aprvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
mayvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
junvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
julvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
augvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
sepvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
octvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
novvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")
decvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface")

@@

  for (td in 1:nrow(unlayer_yr)){
      temp_depth <- raster(unlayer_yr$temp_depth[td])
      crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(temp_depth) <- "temp_depth"
      #temp_depth <- projectRaster(temp_depth, aea)
      chl_surface <- raster(unlayer_yr$chl_depth[td])
      crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(chl_surface) <- "chl_surface"
      #chl_depth <- projectRaster(chl_depth, aea)
      o2_depth <- raster(unlayer_yr$o2_depth[td])
      crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(o2_depth) <- "o2_depth"
      #o2_depth <- projectRaster(o2_depth, aea)
      salinity_depth <- raster(unlayer_yr$salinity_depth[td])
      crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(salinity_depth) <- "salinity_depth"
      #salinity_depth <- projectRaster(salinity_depth, aea)
      # nao_sample <- raster(unlayer_yr$nao_sample[td])
      # crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      # names(nao_sample) <- "nao_sample"
      # nao_sample <- projectRaster(nao_sample, aea)
      # nao_prev <- raster(unlayer_yr$nao_prev[td])
      # crs(nao_prev) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      # names(nao_prev) <- "nao_prev"
      # nao_prev <- projectRaster(nao_prev, aea)
      # nao_winter <- raster(unlayer_yr$nao_winter[td])
      # crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      # names(nao_winter) <- "nao_winter"
      # nao_winter <- projectRaster(nao_winter, aea)
      # amo_sample <- raster(unlayer_yr$amo_sample[td])
      # crs(amo_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      # names(amo_sample) <- "amo_sample"
      # amo_sample <- projectRaster(amo_sample, aea)
      # amo_winter <- raster(unlayer_yr$amo_winter[td])
      # crs(amo_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      # names(amo_winter) <- "amo_winter"
      # amo_winter <- projectRaster(amo_winter, aea)
      stackn <- unlayer_yr$stackname[td]
      stack <- stack(temp_depth, salinity_depth, o2_depth, chl_surface)

>>>>

select month
```{r month of interest -change}
mthna <- "apr"
mthno <- "4"
```

@@

remove all rows with the year 2015 (due to low number of samples)
```{r}
presback <- subset(presback, year!="2015")
```

@@

```{r}
marvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
aprvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
mayvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
junvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
julvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
augvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
sepvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
octvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
novvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")
decvar <- c("occurrence", "year", "temp_depth", "salinity_depth", "o2_depth", "chl_surface", "nao_sample", "nao_prev", "nao_winter", "amo_sample", "amo_winter")

@@

  for (td in 1:nrow(unlayer_yr)){
      temp_depth <- raster(unlayer_yr$temp_depth[td])
      crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(temp_depth) <- "temp_depth"
      #temp_depth <- projectRaster(temp_depth, aea)
      chl_surface <- raster(unlayer_yr$chl_surface[td])
      crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(chl_surface) <- "chl_surface"
      #chl_depth <- projectRaster(chl_depth, aea)
      o2_depth <- raster(unlayer_yr$o2_depth[td])
      crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(o2_depth) <- "o2_depth"
      #o2_depth <- projectRaster(o2_depth, aea)
      salinity_depth <- raster(unlayer_yr$salinity_depth[td])
      crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(salinity_depth) <- "salinity_depth"
      #salinity_depth <- projectRaster(salinity_depth, aea)
      nao_sample <- raster(unlayer_yr$nao_sample[td])
      crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_sample) <- "nao_sample"
      #nao_sample <- projectRaster(nao_sample, aea)
      nao_prev <- raster(unlayer_yr$nao_prev[td])
      crs(nao_prev) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(nao_prev) <- "nao_prev"
      #nao_prev <- projectRaster(nao_prev, aea)
      nao_winter <- raster(unlayer_yr$nao_winter[td])
      crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(nao_winter) <- "nao_winter"
      #nao_winter <- projectRaster(nao_winter, aea)
      amo_sample <- raster(unlayer_yr$amo_sample[td])
      crs(amo_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
      names(amo_sample) <- "amo_sample"
      #amo_sample <- projectRaster(amo_sample, aea)
      amo_winter <- raster(unlayer_yr$amo_winter[td])
      crs(amo_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
      names(amo_winter) <- "amo_winter"
      #amo_winter <- projectRaster(amo_winter, aea)
      stackn <- unlayer_yr$stackname[td]
      stack <- stack(temp_depth, salinity_depth, o2_depth, chl_surface, nao_sample, nao_prev, nao_winter, amo_sample, amo_winter)
